Manuscript results: Forecasting influenza using ARIMA and ARIMAX

### 2025-06-23 manuscript_results.Rmd
update

my_data = read.csv("NHSH_hospitalizations_seed/treated_influenza_hosp_dataframe_v2.csv")
my_data$target_end_date<-as.Date(my_data$target_end_date) # set the dates as dates

@@

```{r}
pop_data <- read.csv("NHSH_hospitalizations_seed/regression_features/population_data.csv") # resident population and population density
sovi_data <- read.csv("NHSH_hospitalizations_seed/regression_features/sovi_2010.2014.csv") # SOVI index
bric_data<-read.csv("NHSH_hospitalizations_seed/regression_features/bric2015.csv") # BRIC index
humidity_data<-read.csv("NHSH_hospitalizations_seed/regression_features/humidity_climatology_1990_2020.csv") # ERA5 Specific Humidity
temperature_data<-read.csv("NHSH_hospitalizations_seed/regression_features/temperature_climatology_1990_2020.csv") # ERA5 Specific Temperature

>>>>

my_data = read.csv("models_with_logback/treated_influenza_hosp_dataframe_v2.csv")
my_data$target_end_date<-as.Date(my_data$target_end_date) # set the dates as dates

@@

```{r}
pop_data <- read.csv("models_with_logback/regression_features/population_data.csv") # resident population and population density
sovi_data <- read.csv("models_with_logback/regression_features/sovi_2010.2014.csv") # SOVI index
bric_data<-read.csv("models_with_logback/regression_features/bric2015.csv") # BRIC index
humidity_data<-read.csv("models_with_logback/regression_features/humidity_climatology_1990_2020.csv") # ERA5 Specific Humidity
temperature_data<-read.csv("models_with_logback/regression_features/temperature_climatology_1990_2020.csv") # ERA5 Specific Temperature
